\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[
    ignoreheadfoot, % set margins without considering header and footer
    top=2 cm, % separation between body and page edge from the top
    bottom=2 cm, % separation between body and page edge from the bottom
    left=2 cm, % separation between body and page edge from the left
    right=2 cm, % separation between body and page edge from the right
    footskip=1.0 cm % separation between body and footer
]{geometry} % for adjusting page geometry
\usepackage{titlesec} % for customizing section titles
\usepackage{tabularx} % for making tables with fixed width columns
\usepackage{array} % tabularx requires this
\usepackage[dvipsnames]{xcolor} % for coloring text
\definecolor{primaryColor}{RGB}{0, 79, 144} % define primary color
\usepackage{enumitem} % for customizing lists
\usepackage{fontawesome5} % for using icons
\usepackage{amsmath} % for math
\usepackage[
    pdftitle={Shubham Kumar Bhokta's CV},
    pdfauthor={Shubham Kumar Bhokta},
    pdfcreator={LaTeX with RenderCV},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref} % for links, metadata and bookmarks
\usepackage[pscoord]{eso-pic} % for floating text on the page
\usepackage{calc} % for calculating lengths
\usepackage{bookmark} % for bookmarks
\usepackage{lastpage} % for getting the total number of pages
\usepackage{changepage} % for one column entries (adjustwidth environment)
\usepackage{paracol} % for two and three column entries
\usepackage{ifthen} % for conditional statements
\usepackage{needspace} % for avoiding page break right after the section title
\usepackage{iftex} % check if engine is pdflatex, xetex or luatex

% Ensure that generated PDF is machine readable/ATS parsable:
\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

% Some settings:
\pagestyle{empty} % no header or footer
\setcounter{secnumdepth}{0} % no section numbering
\setlength{\parindent}{0pt} % no indentation
\setlength{\topskip}{0pt} % no top skip
\setlength{\columnsep}{0cm} % set column separation
\titleformat{\section}{\needspace{4\baselineskip}\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{-1pt}{0.3 cm}{0.2 cm} % section title spacing

\renewcommand\labelitemi{$\circ$} % custom bullet points

\begin{document}

\begin{center}
    \textbf{\huge Shubham Kumar Bhokta} \\[0.5em]
    \textit{Undergraduate at Indian Institute of Information Technology, Allahabad} \\[0.5em]
    \href{mailto:jnvshubham7@gmail.com}{jnvshubham7@gmail.com} | 
    +91 6299360050 | 
    Madhupur, India \\
    \href{https://linkedin.com/in/shubham-kumar-bhokta-97113116b}{LinkedIn} | 
    \href{https://github.com/jnvshubham7}{GitHub} | 
    \href{https://shubhambhokta.vercel.app/}{Portfolio}
\end{center}

% ----- EXPERIENCE -----
\section{EXPERIENCE}

\textbf{Full Stack Developer}, CG Viz Studio \hfill 10/2024 -- Present \\
Remote
\begin{highlightsforbulletentries}
    \item Developing a 3D modeling calculator with complex calculations, writing and improving JavaScript logic for an ongoing 3D viewer project, and utilizing PHP for backend tasks like email handling.
    \item Collaborating with the design team to enhance UI and user experience.
\end{highlightsforbulletentries}
\item 
\textbf{Technologies Used:} HTML, CSS, JavaScript, PHP

\vspace{1em}

\textbf{SDE Intern (Flutter)}, Tandem \hfill 06/2024 -- 08/2024 \\
\textit{Remote} \\
\begin{highlightsforbulletentries}
    \item Developed and enhanced features for an enterprise-level Flutter application, focusing on document management and real-time vehicle tracking, while leading performance optimizations that significantly reduced app loading times.
    \item Implemented custom UI elements, such as bottom sheets, expansion tiles, and search functionalities, to improve code maintainability, readability, and user interaction.
    \item Worked on the backend to create and integrate REST APIs using Spring Boot, ensuring seamless communication between the front-end and back-end.
    \item Integrated Google Maps and Firebase for real-time vehicle tracking, collaborating closely with the backend team for seamless REST API integration.
    \item Utilized Git for efficient version control and collaboration with the development team.
\end{highlightsforbulletentries}
\textbf{Technologies Used:} Dart, Flutter, Material UI, Firebase, Spring Boot

\vspace{1em}

\textbf{Executive of App Development},  Effervescence IIIT Allahabad \hfill 09/2021 -- 11/2021 \\
Remote
\begin{highlightsforbulletentries}
    \item Led the app development team for the college cultural fest.
    \item Collaborated with a group to create an Android app, enhancing user engagement during the event.
\end{highlightsforbulletentries}
\item
\textbf{Technologies Used:} Java, Android, Firebase, Android Studio \\
\textit{Project Link:} \href{https://github.com/jnvshubham7/Effervescence_21_CA}{Effervescence}


% ----- PROJECTS -----
\section{PROJECTS}

\textbf{ChatsApp} \hfill 05/2021 -- Present \\
\href{https://github.com/jnvshubham7/ChatsApp}{GitHub} \\
\begin{highlightsforbulletentries}
    Developed an Android app, available on the Mi App Store with over 115+ users. Features include free messaging, story sharing, photo sending, and real-time notifications.
    \item \textbf{Technology Used}: Java, Xml, Android, Firebase, Android Studio
    \item \textit{App Link:} \href{https://global.app.mi.com/details?lo=IN&la=en_US&id=com.example.chatsapp}{ChatsApp}
\end{highlightsforbulletentries}

\vspace{2em}

\textbf{Techie Notes} \hfill 08/2024 -- Present 

\begin{highlightsforbulletentries}
     Web app offering articles, notes, and tutorials on tech and software development.
     Integrated \textbf{TechieGPT}: AI assistant for tech-related queries.
    \item \textbf{Technologies}: HTML, CSS, JavaScript, React, Firebase, Groq API.
    \item \textit{WebLink:} \href{https://techienotes.vercel.app}{Techie Notes}
\end{highlightsforbulletentries}


% ----- EDUCATION -----
\section{EDUCATION}

\textbf{B.Tech in Information Technology} \hfill 2020 -- 2024 \\
Indian Institute of Information Technology, Allahabad \\
CGPA: 8.05


% ----- SKILLS -----
\section{SKILLS}

\textbf{Experienced:} C++, Java, Dart, Flutter Dev, App Dev, Web Dev \\[0.5em]
\textbf{Familiar:} C, Python, JavaScript, React, HTML, CSS, Dart \\[0.5em]
\textbf{Relevant Coursework:} DSA, CN, OOPs, DBMS, OS \\[0.5em]
\textbf{Technologies:} Flutter, Firebase Database, Git, VS Code, Android Studio, Vercel \\[0.5em]
\textbf{Interest:} Coding (DSA), Android Development, Web Development, Flutter Development

% ----- CODING PROFILE -----
\section{CODING PROFILE}

\textit{\textbf{Leetcode:}} (700+ Questions Solved) \\
Profile Link: \href{https://leetcode.com/jnvshubham7/}{jnvshubham7}

\vspace{1em}

\textit{\textbf{GeeksforGeeks:}} (350+ Questions Solved) \\
Profile Link: \href{https://auth.geeksforgeeks.org/user/jnvshubham7/profile}{jnvshubham7}


\end{document}
